Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-02-07 vesicle_code/docs/adhesion/adhesion.tex
some minor changes from yny

The dynamics of adhesive vesicles under various flowing
conditions is investigated numerically using a high-order
adaptive-in-time boundary integral equation formulation. In a quiescent
flow, two nearby vesicles move slowly towards each other under the adhesive
potential, pushing out fluid in the gap to form a doublet at
equilibrium. A lubrication analysis on such draining of the thin film
gives the dependencies of draining time on adhesion strength and
separation distance that are in good agreement with numerical results.
%
In a microfluid trap where the stagnation of an extensional flow is
placed in the middle of a vesicle doublet through an active control
loop, novel dynamics of a vesicle doublet are observed. Numerical
simulations show that there exists a critical extensional flow rate
above which the weak adhesive interaction is overcome by the
hydrodynamic diverging stream, thus providing a simple method to measure
the adhesion strength between two vesicle membranes. 
%
In a planar shear flow, numerical simulations reveal that a vesicle
doublet may form as they approach each other provided that the adhesion
strength is sufficient large at a given vesicle reduced area. Once a
doublet is formed, the effective shear viscosity of a dilute suspension
of vesicle doublets is found to be a function of both reduced area and
the adhesion strength.  Results from these numerical studies and
analysis shed light on the hydrodynamic effects of adhesive interactions
between vesicles in a viscous fluid.
%\begin{description}
%\item[Usage]
%Secondary publications and information retrieval purposes.
%\item[PACS numbers]
%May be entered using the \verb+\pacs{#1}+ command.
%\item[Structure]
%You may use the \texttt{description} environment to structure your abstract;
%use the optional argument of the \verb+\item+ command to give the category of each item. 
%\end{description}
\end{abstract}

@@

\section{Introduction}
Vesicles (closed fluid-filled phospholipid bilayer membranes) have been
widely utilized as biological cell mimics in biophysics and material
engineering \cite{sackmann1996,Barthes-Biesel2016_ARFM}.  The ever expanding applications have
encouraged detailed experimental, theoretical, and numerical
investigations of vesicle hydrodynamics in applied flow, electric
fields, and magnetic fields.  Theoretical investigations often take the
form of small-deformation analysis or spheroidal dynamics of a
nearly-spherical vesicle (or nearly-circular in two dimensions)
subjected to an applied flow or under an external
forcing~\cite{Barthes-BieselRallison1981_JFM, Misbah2006_PRL,
Vlahovska2007_PRE, Finken2008_EPL, ZhangZahnTanLin2013_PoF,
Nganguia2013_PRE}.  On the other hand, various numerical methods have
been developed for simulating the transient hydrodynamics of vesicle
suspensions~\cite{BagchiJohoson2005_JBE, Biben2005_EJP,
Veerapaneni2009_JCP, SeolHuKimLai2016_JCP}.

@@

Collective hydrodynamics of vesicles is dictated by the vesicle-vesicle
interactions.  In a quiescent flow, vesicle-vesicle adhesion leads to
the formation of vesicle doublets~\cite{Ziherl2007_PRL,
ZiherlSvetina2007_PNAS} or clusters
\cite{SvetinaZiherl2008_Bioelectrochemistry,
FlormannAouane2017_SciReports}.  As a model for red blood cell (RBC)
aggregates, an idealized model for adhesive vesicle-vesicle interactions
gives rise to vesicle configurations similar to those observed in
experiments of fibrinogen-induced RBC
aggregates~\cite{SvetinaZiherl2008_Bioelectrochemistry,
FlormannAouane2017_SciReports}.  Using the Lennard-Jones (L-J) potential
for point-point interaction between two vesicle membranes without the
molecular details of adhesive interactions between RBCs, Flormann {\em
et al.}~found the contact zone to buckle under strong
adhesion~\cite{FlormannAouane2017_SciReports}.  A direct consequence of
the buckling is the sigmoidal shape of the adhesion region, which is
also observed in RBC doublets and explained in a slightly different
model~\cite{ZiherlSvetina2007_PNAS}.  It remains unknown how adhesive
interactions between vesicles might lead to different vesicle
hydrodynamics that results in different rheological properties of a
vesicle suspension. Such studies will provide useful insight to the
rheology of blood flow and how to use nano solutes to control the
hypertension by adjusting the adhesive interactions between RBCs.

@@

The electrostatic nature of lipid molecules (a hydrophobic tail and a
hydrophilic head with an electric dipole) complicates the interactions
between a lipid bilayer membrane and another bilayer
membrane~\cite{EvansMetcalfe1984_BJ, Book_PhysicalBasisCellAdhesion,
Book_IntermolecularSurfaceForces, PerutkovaFrank-Bertoncelij2013_CSB} or
a solid (such as a glass substrate or a nano particle).  Adhesion
between a vesicle and a substrate has been extensively studied with more
focuses on the static equilibrium shapes~\cite{Seifert1990_PRA,
ShiFengGao2006_ActaMechSin, LinFreund2007_IntJSolidsStructures,
GruhnFrankeDimova2007_Langmuir,das2008adhesion, zhang2009phase,
SteinkuhlerAgudo-Canalejo2016_BJ} than the transient adhesion
process~\cite{cantat1999lift, suk-sei2001, BlountMiksisDavis2013_PRSa}.
Adhesive interactions between lipid membranes are essential in many
biomedical, biological, and biophysical processes.  For example, vesicle
adhesion is crucial to initiate membrane fusion and fission in
endocytosis and exocytosis, the transport of small vesicles through
membrane surfaces.  In the absence of an external electric field and
ions in the solvents, it is reported that the adhesive interactions
between two membranes can be well approximated by the L-J-type
potential~\cite{FlormannAouane2017_SciReports}, that consists of a
long-range attraction component and a short-range repulsion
component~\cite{Book_IntermolecularSurfaceForces}, and the combination
of the two gives rise to adhesion at the separation distance that
minimizes the interaction
potential~\cite{Book_IntermolecularSurfaceForces}.

@@

This paper is organized as follows. In Section~\ref{sec:ge} we formulate
our model for two-dimensional vesicle hydrodynamics with adhesive
interactions between membranes of distinct vesicles.  We simulate the
adhesion process of two vesicles in a quiescent flow in
Section~\ref{sec:qflow}, where we also present a simple model to
estimate how long it takes for two nearby vesicles to reach an
equilibrium configuration under adhesion. In Section~\ref{sec:eflow} we
numerically investigate the hydrodynamics of a vesicle doublet in a
fluid trap where the stagnation point is actively controlled to be at
the center of the vesicle doublet. From these results we propose a novel
application of the microfluidic fluid trap to probe the adhesion
strength between lipid bilayer membranes in solutions. In
Section~\ref{sec:sflow} we investigate how two vesicles may form a
doublet as they move toward each other under a planar shear flow.  We
map out the parameter regions for bound/unbound vesicles under a planar
shear flow, and we also investigate the effects of adhesive interactions
on the rheological properties of a dilute suspension of vesicle
doublets.  Finally in Section~\ref{sec:conclusions} we discuss the
implications of our results and point out a few potential future
directions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Governing Equations \label{sec:ge}}
We consider suspensions of locally inextensible vesicles in an unbounded
two-dimensional viscous fluid.  For simplicity, we assume the fluid
viscosity both inside and outside the vesicles is constant, but our
method can be easily adjusted to account for a viscosity contrast.
Individual vesicles are denoted as $\gamma_j$, and they are
parameterized in arclength as $\xx_j(s,t)$.  The union of all vesicles
is denoted by $\gamma$.  Given a background velocity $\uu_\infty$, the
governing equations are
\begin{equation*}
\begin{aligned}
  \mu \Delta \uu = \nabla p, \quad &\xx \in \RR^2,
    &&\mbox{\em conservation of momentum} \\
  \nabla \cdot \uu = 0, \quad &\xx \in \RR^2, 
    &&\mbox{\em conservation of mass} \\
  \uu \rightarrow \uu_\infty, \quad &\|\xx\| \rightarrow \infty,
    &&\mbox{\em far-field condition} \\
  \uu(\xx,t) = \dot{\xx}, \quad &\xx \in \gamma,
    &&\mbox{\em velocity continuity} \\
  \xx_s \cdot \uu_s =0, \quad &\xx \in \gamma,
    &&\mbox{\em local inextensibility} \\
  \llbracket T \rrbracket \nn = \xxi, \quad &\xx \in \gamma,
    &&\mbox{\em non-zero traction jump}
\end{aligned}
\end{equation*}
where $\xxi$ is the traction jump that is the sum of the bending,
stretching, and adhesion forces.  The bending term $\BB \xx = -\kappa_b
\xx_{ssss}$ comes from the Helfrich energy, where $\kappa_b$ is the
bending modulus and $s$ is arclength.  For the numerical examples, we
set $\kappa_b = 1$ and consider adhesion strengths ranging from $0.1$ to
$1$ times the bending modulus.  The stretching term is $\TT \sigma  =
(\sigma \xx_s)_s$, where $\sigma$ is the tension, and the tension acts
as a Lagrange multiplier to satisfy the local extensibility constraint.
The resistance to bending and stretching are standard assumptions of
vesicles.  In this work, we include an adhesive term, $\AA \xx$, that we
now describe.

@@

The exponents $(m,n)$ depend on the geometry of the two objects under
adhesion~\cite{Book_IntermolecularSurfaceForces}: $(m,n)=(4,2)$
corresponds to two flat, planar surfaces interacting with each under a
long-range attraction and a short-range repulsion. On the other hand,
$(m,n) = (12,6)$ corresponds to the L-J potential between two molecules.
In our case, the adhesion potential in the integral of
equation~\eqref{eqn:adhesionForce} is between two small patches of lipid
bilayer membrane (because the lipid molecules are coarse-grained in the
continuum modeling).  Thus a reasonable choice for $(m,n)$ between two
coarse-grained membrane patches would be between those for two planar
surfaces and two point molecules.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in a quiescent flow} 
\label{sec:qflow} 
We consider the suspension of two identical two-dimensional vesicles
suspended in a quiescent flow.  Without any external forcing such as an imposed
electric field or a fluid flow in the far-field, the long-range
attraction pulls two vesicles together until their separation distance
is close to $\delta$.  In Section~\ref{subsec:qflow_draining_times}, we
compute the expected time for the vesicles to reach an equilibrium
configuration and compare the analysis with numerical simulations.  In
Section~\ref{subsec:qflow_adhesion_parameters}, we characterize the
effects of the adhesion parameters and the vesicles' reduced area on the
bending and adhesive energies.

@@

\begin{figure}
\includegraphics[keepaspectratio=true,scale=0.4]{figs/Dec13a_time_scaling01.png}
\includegraphics[keepaspectratio=true,scale=0.4]{figs/Dec13a_time_scaling02.png}
\caption{\label{fig:qflow00} Scaling of the time it takes for two
  vesicles to reach equilibrium. {\em Left}: Scaling with respect to
  $\delta$ with $\mathcal{H}=0.1$.  {\em Right}: Scaling with respect to
  $\mathcal{H}$ with
  $\delta = 0.4$. Arrows indicate the time by when the equilibrium is
  reached within $1\%$.}
  \todo[inline]{Change the $H$ in the right figure to $\mathcal{H}$}
\end{figure}

@@

In this work we focus on weakly adhesive vesicles whose equilibrium
shapes in a quiescent flow are shown in the left plot of
Figure~\ref{fig:Dec18_vesicle_shape} for three reduced areas: $\Delta
A=0.95$, $0.75$, and $0.6$ with $\mathcal{H}=5$ and $\delta = 0.2$. 
\begin{figure}
  \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_00.jpeg}
  \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_01.jpeg}
  \caption{\label{fig:Dec18_vesicle_shape} Two vesicles of the same length, reduced area
  and bending rigidity ($\kappa=1$)
  with $\mathcal{H}=5$, and $\delta=0.2$.  {\em Left}:
  Equilibrium shapes of two vesicles under adhesive interactions with
  adhesion strength $\mathcal{H}=5$ and separation distance
  $\delta=0.2$.  Vesicle reduced area $\Delta A=0.95$, $0.75$, and $0.6$
  are labeled.  The color coding is the tension along the vesicle. {\em
  Right}: Membrane shapes in the contact region.} \todo[inline]{This
  caption contradicts itself.  Is it $\mathcal{H} = 0.5$ or $\mathcal{H}
  = 5$?}
\end{figure}
The equilibrium vesicle shape for $\Delta A=0.95$ is the circular cap
with a flat contact region.  This is similar to the observed shapes of
two vesicles under strong adhesive interaction
in~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.  When
vesicles are more deflated with a reduced area $\Delta A = 0.75$, the
equilibrium vesicle shape is elongated with a bigger contact region.
This is consistent with the equilibrium shapes of a vesicle doublet
under a L-J potential ($(m,n) =
(12,6)$)~\cite{FlormannAouane2017_SciReports}.  As the reduced area
decreases further, we observe undulation of the elongated equilibrium
vesicle shape on the non-contact side while the contact region remains
flat.  The color coding along each curve is the tension of the vesicle
membrane.  We observe that the membrane tension in the contact region is
very negative, indicating a dominant compression of membrane when the
adhesion force is strong to keep the vesicles bound together.

@@

\begin{figure}
\includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_Ebleft_Eadhright_vs_rA_adR0p2_adS502.jpeg}
\includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_EbEadh_vs_rA_adR0p2_adS502.jpeg}
  \caption{\label{fig:Dec18_vesicle_equilibrium1} Two vesicles of the same length, reduced area
  and bending rigidity ($\kappa=1$)  with $\mathcal{H}=5$ and $\delta=0.2$.  {\em Left}:
  Total bending energy (solid curve) and adhesion energy (dash-dotted
  curve) plotted against the reduced area $\Delta A$. {\em Right}: Sum
  of two energies plotted against reduced area $\Delta A$.}
\end{figure}

@@

\begin{figure}
\includegraphics[keepaspectratio=true,scale=0.18]{figs/Dec18_Eb_vs_sigma_rA0p9502.jpeg}
\includegraphics[keepaspectratio=true,scale=0.18]{figs/Dec18_Eadh_vs_sigma_rA0p9502.jpeg}
  \caption{\label{fig:Dec18_equilibrium} Total bending energy (\em left)
  and adhesion energy {\em right} versus the adhesion strength
  $\mathcal{H}$ for two vesicles with reduced area $\Delta A=0.95$,
  separation distance $\delta = 0.2$ (triangles), $0.3$ (crosses), and
  $0.4$ (circles).}
  \todo[inline]{Change $H$ to $\mathcal{H}$ in the x-axis.}
\end{figure}

@@

We begin with two vesicles identical vesicles forming a doublet under an
adhesion potential in a quiescent flow as described in
Section~\ref{sec:qflow}.  Once a doublet forms and reaches an
equilibrium configuration, we turn on the fluid trap with the stagnation
point placed at the center of the vesicle doublet.  At low extensional
rates, $\chi$, we expect the vesicle doublet to stay fixed at the fluid
trap stagnation point.  On the other hand, the vesicle doublet may
become unstable and eventually separate at higher extensional rates.
Thus we expect there to exist a critical extensional rate above which
the vesicle doublet cannot stay bound under a given adhesion potential.
Therefore, the dependence of the critical extensional rate on the
adhesion potential and the mechanical vesicle properties provides a
means to probe the physics of membrane adhesion.

@@

We also examine how adhesive interaction may lead to formation of a
vesicle doublet dynamically in flowing conditions.  We simulate two
vesicles approaching each other in a planar shear flow, and examine how
their adhesive interactions lead to doublet formation.  Once a doublet
forms, the two vesicle membranes rotate around each other as they deform
dynamically. The usual tank-treading motion of a vesicle under shear
flow is not observed in each of the two vesicles. We compute the
effective shear viscosity of a dilute suspension of vesicle doublets,
and found it to be more than twice the effective shear viscosity of a dilute suspension of single vesicles.
Furthermore, we find that the membrane adhesion contribution to the shear viscosity increases with decreasing
reduced area while the bending/tension contribution increases with the reduced area.
%
%because deflated vesicles (low reduced area) deform more
%easily and more membranes in the contact region.
\todo[inline]{I don't understand this last sentence --> modified now by yny}

>>>>

The dynamics of adhesive vesicles under various flowing
conditions is investigated numerically using a high-order
adaptive-in-time boundary integral equation formulation. In a quiescent
flow, two nearby vesicles move slowly towards each other under the adhesive
potential, pushing out fluid between them to form a doublet at
equilibrium. A lubrication analysis on such draining of the thin film
gives the dependencies of draining time on adhesion strength and
separation distance that are in good agreement with numerical results.
%
In a microfluid trap where the stagnation of an extensional flow is
placed in the middle of a vesicle doublet through an active control
loop, novel dynamics of a vesicle doublet are observed. Numerical
simulations show that there exists a critical extensional flow rate
above which adhesive interaction is overcome by the
hydrodynamic diverging stream, thus providing a simple method to measure
the adhesion strength between two vesicle membranes. 
%
In a planar shear flow, numerical simulations reveal that a vesicle
doublet may form as they approach each other provided that the adhesion
strength is sufficient large at a given vesicle reduced area. Once a
doublet is formed, the effective shear viscosity of a dilute suspension
of vesicle doublets is found to be a function of both reduced area and
the adhesion strength.  Results from these numerical studies and
analysis shed light on the hydrodynamic effects of adhesive interactions
between vesicles in a viscous fluid.
%\begin{description}
%\item[Usage]
%Secondary publications and information retrieval purposes.
%\item[PACS numbers]
%May be entered using the \verb+\pacs{#1}+ command.
%\item[Structure]
%You may use the \texttt{description} environment to structure your abstract;
%use the optional argument of the \verb+\item+ command to give the category of each item. 
%\end{description}
\end{abstract}

@@

\section{Introduction}
Vesicles (closed fluid-filled phospholipid bilayer membranes) have been
widely utilized as biological cell mimics in biophysics and material
engineering \cite{sackmann1996,Barthes-Biesel2016_ARFM}.  The ever expanding applications have
encouraged novel experimental, theoretical, and numerical
investigations of vesicle hydrodynamics in applied flow, electric
fields, and magnetic fields.  Theoretical investigations often take the
form of small-deformation analysis or spheroidal dynamics of a
nearly-spherical vesicle (or nearly-circular in two dimensions)
subjected to an applied flow or under an external
forcing~\cite{Barthes-BieselRallison1981_JFM, Misbah2006_PRL,
Vlahovska2007_PRE, Finken2008_EPL, ZhangZahnTanLin2013_PoF,
Nganguia2013_PRE}.  On the other hand, various numerical methods have
been developed for simulating the transient hydrodynamics of vesicle
suspensions~\cite{BagchiJohoson2005_JBE, Biben2005_EJP,
Veerapaneni2009_JCP, SeolHuKimLai2016_JCP}.

@@

Collective hydrodynamics of vesicles is dictated by the vesicle-vesicle
interactions.  In a quiescent flow, vesicle-vesicle adhesion leads to
the formation of vesicle doublets~\cite{Ziherl2007_PRL,
ZiherlSvetina2007_PNAS} or clusters
\cite{SvetinaZiherl2008_Bioelectrochemistry,
FlormannAouane2017_SciReports}.  As a model for red blood cell (RBC)
aggregates, an idealized model for adhesive vesicle-vesicle interactions
gives rise to vesicle configurations similar to those observed in
experiments of fibrinogen-induced RBC
aggregates~\cite{SvetinaZiherl2008_Bioelectrochemistry,
FlormannAouane2017_SciReports}.  Using the Lennard-Jones (L.-J.) potential
for point-point interaction between two vesicle membranes without the
molecular details of adhesive interactions between RBCs, Flormann {\em
et al.}~found the contact zone to buckle under strong
adhesion~\cite{FlormannAouane2017_SciReports}.  A direct consequence of
the buckling is the sigmoidal shape of the adhesion region, which is
also observed in RBC doublets and explained in a slightly different
model~\cite{ZiherlSvetina2007_PNAS}.  It remains unknown how adhesive
interactions between vesicles might lead to different vesicle
hydrodynamics that results in different rheological properties of a
vesicle suspension. Such studies will provide useful insight to the
rheology of blood flow and how to use nano solutes to control the
hypertension by adjusting the adhesive interactions between RBCs.

@@

The electrostatic nature of lipid molecules (a hydrophobic tail and a
hydrophilic head with an electric dipole) complicates the interactions
between a lipid bilayer membrane and another bilayer
membrane~\cite{EvansMetcalfe1984_BJ, Book_PhysicalBasisCellAdhesion,
Book_IntermolecularSurfaceForces, PerutkovaFrank-Bertoncelij2013_CSB} or
a solid (such as a glass substrate or a nano particle).  Adhesion
between a vesicle and a substrate has been extensively studied with more
focuses on the static equilibrium shapes~\cite{Seifert1990_PRA,
ShiFengGao2006_ActaMechSin, LinFreund2007_IntJSolidsStructures,
GruhnFrankeDimova2007_Langmuir,das2008adhesion, zhang2009phase,
SteinkuhlerAgudo-Canalejo2016_BJ} than the transient adhesion
process~\cite{cantat1999lift, suk-sei2001, BlountMiksisDavis2013_PRSa}.
Adhesive interactions between lipid membranes are essential in many
biomedical, biological, and biophysical processes.  For example, vesicle
adhesion is crucial to initiate membrane fusion and fission in
endocytosis and exocytosis, the transport of small vesicles through
membrane surfaces.  In the absence of an external electric field and
ions in the solvents, it is reported that the adhesive interactions
between two membranes can be well approximated by the L.-J.-type
potential~\cite{FlormannAouane2017_SciReports}, that consists of a
long-range attraction component and a short-range repulsion
component~\cite{Book_IntermolecularSurfaceForces}, and the combination
of the two gives rise to adhesion at the separation distance that
minimizes the interaction
potential~\cite{Book_IntermolecularSurfaceForces}.

@@

This paper is organized as follows. In Section~\ref{sec:ge} we formulate
our model for two-dimensional vesicle hydrodynamics with adhesive
interactions between membranes of distinct vesicles.  We simulate the
adhesion process of two vesicles in a quiescent flow in
Section~\ref{sec:qflow}, where we also present a simple lubrication model to
estimate how long it takes for two nearby vesicles to reach the
separation distance set by the adhesion potential.
In Section~\ref{sec:eflow} we
numerically investigate the hydrodynamics of a vesicle doublet in a
fluid trap where the stagnation point is actively controlled to be at
the center of the vesicle doublet. From these results we propose a novel
application of the microfluidic fluid trap to probe the adhesion
strength between lipid bilayer membranes in solutions. In
Section~\ref{sec:sflow} we investigate how two vesicles may form a
doublet as they move toward each other under a planar shear flow.  We
map out the parameter regions for bound/unbound vesicles under a planar
shear flow, and we also investigate the effects of adhesive interactions
on the rheological properties of a dilute suspension of vesicle
doublets.  Finally in Section~\ref{sec:conclusions} we discuss the
implications of our results and point out a few potential future
directions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Governing Equations \label{sec:ge}}
We consider suspensions of locally inextensible vesicles in an unbounded
two-dimensional viscous fluid.  For simplicity, we assume the fluid
viscosity both inside and outside the vesicles is constant, but our
method can be easily adjusted to account for a viscosity contrast.
Individual vesicles are denoted as $\gamma_j$, and they are
parameterized in arclength as $\xx_j(s,t)$.  The union of all vesicles
is denoted by $\gamma$.  Given a background velocity $\uu_\infty$, the
governing equations are
\begin{equation*}
\begin{aligned}
  \mu \Delta \uu = \nabla p, \quad &\xx \in \RR^2,
    &&\mbox{\em conservation of momentum} \\
  \nabla \cdot \uu = 0, \quad &\xx \in \RR^2, 
    &&\mbox{\em conservation of mass} \\
  \uu \rightarrow \uu_\infty, \quad &\|\xx\| \rightarrow \infty,
    &&\mbox{\em far-field condition} \\
  \uu(\xx,t) = \dot{\xx}, \quad &\xx \in \gamma,
    &&\mbox{\em velocity continuity} \\
  \xx_s \cdot \uu_s =0, \quad &\xx \in \gamma,
    &&\mbox{\em local inextensibility} \\
  \llbracket T \rrbracket \nn = \xxi, \quad &\xx \in \gamma,
    &&\mbox{\em non-zero traction jump}
\end{aligned}
\end{equation*}
where $\xxi$ is the traction jump that is the sum of the bending,
stretching, and adhesion forces.  The bending term $\BB \xx = -\kappa_b
\xx_{ssss}$ comes from the Helfrich energy, where $\kappa_b$ is the
bending rigidity modulus and $s$ is arclength.  For the numerical examples, we
set $\kappa_b = 1$ and consider adhesion strengths ranging from $0.1$ to
$1$ times the bending rigidity modulus.  The stretching term is $\TT \sigma  =
(\sigma \xx_s)_s$, where $\sigma$ is the tension, and the tension acts
as a Lagrange multiplier to satisfy the local extensibility constraint.
The resistance to bending and stretching are standard assumptions of
vesicles.  In this work, we include an adhesive term, $\AA \xx$, that we
now describe.

@@

The exponents $(m,n)$ depend on the geometry of the two objects under
adhesion~\cite{Book_IntermolecularSurfaceForces}: $(m,n)=(4,2)$
corresponds to two flat, planar surfaces interacting with each under a
long-range attraction and a short-range repulsion. On the other hand,
$(m,n) = (12,6)$ corresponds to the L.-J. potential between two molecules.
In our case, the adhesion potential in the integral of
equation~\eqref{eqn:adhesionForce} is between two small patches of lipid
bilayer membrane (because the lipid molecules are coarse-grained in the
continuum modeling).  Thus a reasonable choice for $(m,n)$ between two
coarse-grained membrane patches would be between those for two planar
surfaces and two point molecules.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in a quiescent flow} 
\label{sec:qflow} 
We consider the suspension of two identical two-dimensional vesicles
suspended in a quiescent flow.  Without any external forcing such as an imposed
electric field or a fluid flow in the far-field, the long-range
attraction pulls two vesicles together until their separation distance
is close to $\delta$ and large deformation occurs in the ``contact region". The L.-J. type potential prohibits
physical contact between two membranes and instead keep them close to the separation distance $\delta$.
In Section~\ref{subsec:qflow_draining_times}, we
compute the expected time for the vesicles to reach an equilibrium
configuration and compare the analysis with numerical simulations.  In
Section~\ref{subsec:qflow_adhesion_parameters}, we characterize the
effects of the adhesion parameters and the vesicles' reduced area on the
bending and adhesive energies.

@@

\begin{figure}
\includegraphics[keepaspectratio=true,scale=0.4]{figs/Dec13a_time_scaling01.png}
\includegraphics[keepaspectratio=true,scale=0.4]{figs/Dec13a_time_scaling02.png}
\caption{\label{fig:qflow00} Scaling of the time it takes for two
  vesicles to reach equilibrium. {\em Left}: Scaling with respect to
  $\delta$ with $\mathcal{H}=0.1$.  {\em Right}: Scaling with respect to
  $\mathcal{H}$ with
  $\delta = 0.4$. Arrows indicate the time by when the equilibrium is
  reached within $1\%$.}
%  \todo[inline]{Change the $H$ in the right figure to $\mathcal{H}$}
\end{figure}

@@

In this work we focus on weakly adhesive vesicles whose equilibrium
shapes in a quiescent flow are shown in the left plot of
Figure~\ref{fig:Dec18_vesicle_shape} for three reduced areas: $\Delta
A=0.95$, $0.75$, and $0.6$ with $\mathcal{H}=5$ and $\delta = 0.2$. 
\begin{figure}
  \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_00.jpeg}
  \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_01.jpeg}
  \caption{\label{fig:Dec18_vesicle_shape} Equilibrium configuration of a doublet of 
  identical vesicles under adhesion in a quiescent flow. Vesicle reduced area $\Delta A=0.95$, $0.75$, and $0.6$
  are labeled.  The color coding is the tension along the vesicle. 
  Vesicle length is fixed at $2\pi$, (dimensionless) bending rigidity modulus $\kappa=1$, $\mathcal{H}=5$, and $\delta=0.2$.
  {\em Left}: Overall
  equilibrium shapes of two vesicles under adhesive interactions vary with reduced area.  
  {\em Right}: Membrane shapes in the contact region.} 
%  \todo[inline]{This
%  caption contradicts itself.  Is it $\mathcal{H} = 0.5$ or $\mathcal{H}
%  = 5$?}
\end{figure}
The equilibrium vesicle shape for $\Delta A=0.95$ is the circular cap
with a flat contact region.  This is similar to the observed shapes of
two vesicles under strong adhesive interaction
in~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.  When
vesicles are more deflated with a reduced area $\Delta A = 0.75$, the
equilibrium vesicle shape is elongated with a bigger contact region.
This is consistent with the equilibrium shapes of a vesicle doublet
under a L.-J. potential ($(m,n) =
(12,6)$)~\cite{FlormannAouane2017_SciReports}.  As the reduced area
decreases further, we observe undulation of the 
vesicle membrane on the non-contact side while the contact region remains
flat.  The color coding along each curve is the tension of the vesicle
membrane.  We observe that the membrane tension in the contact region is
very negative, indicating a dominant compression of membrane when the
adhesion force is strong to keep the vesicles bound together.

@@

\begin{figure}
\includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_Ebleft_Eadhright_vs_rA_adR0p2_adS502.jpeg}
\includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_EbEadh_vs_rA_adR0p2_adS502.jpeg}
  \caption{\label{fig:Dec18_vesicle_equilibrium1}   {\em Left}:
  Total bending energy (solid curve) and adhesion energy (dash-dotted
  curve) plotted against the reduced area $\Delta A$. {\em Right}: Sum
  of two energies plotted against reduced area $\Delta A$. Two vesicles in the doublet are of the same length, reduced area
  and bending rigidity modulus ($\kappa=1$) with $\mathcal{H}=5$ and $\delta=0.2$.}
\end{figure}

@@

\begin{figure}
\includegraphics[keepaspectratio=true,scale=0.18]{figs/Dec18_Eb_vs_sigma_rA0p9502.jpeg}
\includegraphics[keepaspectratio=true,scale=0.18]{figs/Dec18_Eadh_vs_sigma_rA0p9502.jpeg}
  \caption{\label{fig:Dec18_equilibrium} 
  Total bending energy ({\em left})
  and adhesion energy ({\em right}) of a vesicle doublet at equilibrium versus the adhesion strength
  $\mathcal{H}$.  The two vesicles in the doublet have the same length and reduced area $\Delta A=0.95$, with 
  separation distance $\delta = 0.2$ (triangles), $0.3$ (crosses), and
  $0.4$ (circles).}
%  \todo[inline]{Change $H$ to $\mathcal{H}$ in the x-axis.}
\end{figure}

@@

We begin with two identical vesicles forming a doublet under an
adhesion potential in a quiescent flow as described in
Section~\ref{sec:qflow}.  Once a doublet forms and reaches an
equilibrium configuration, we turn on the fluid trap with the stagnation
point placed at the center of the vesicle doublet.  At low extensional
rates, $\chi$, we expect the vesicle doublet to stay fixed at the fluid
trap stagnation point.  On the other hand, the vesicle doublet may
become unstable and eventually separate at higher extensional rates.
Thus we expect there to exist a critical extensional rate above which
the vesicle doublet cannot stay bound under a given adhesion potential.
Therefore, the dependence of the critical extensional rate on the
adhesion potential and the mechanical vesicle properties provides a
means to probe the physics of membrane adhesion.

@@

We also examine how adhesive interaction may lead to formation of a
vesicle doublet dynamically in flowing conditions.  We simulate two
vesicles approaching each other in a planar shear flow, and examine how
their adhesive interactions lead to doublet formation.  Once a doublet
forms, the two vesicle membranes rotate around each other as they deform
dynamically. The usual tank-treading motion of a vesicle under shear
flow is not observed in each of the two vesicles. We compute the
effective shear viscosity of a dilute suspension of vesicle doublets,
and found it to be more than twice the effective shear viscosity of a dilute suspension of single vesicles.
Furthermore, we find that the membrane adhesion contribution to the shear viscosity increases with decreasing
reduced area while the bending/tension contribution increases with the reduced area.
%
%because deflated vesicles (low reduced area) deform more
%easily and more membranes in the contact region.
%\todo[inline]{I don't understand this last sentence --> modified now by yny}
